%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template License:
% Copyright (c) <2018> <Jan Vorisek>

% Permission is hereby granted, free of charge, to any person
% obtaining a copy of this software and associated documentation
% files (the "Software"), to deal in the Software without
% restriction, including without limitation the rights to use,
% copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the
% Software is furnished to do so, subject to the following
% conditions:

% The above copyright notice and this permission notice shall be
% included in all copies or substantial portions of the Software.

% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
% EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
% OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
% NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
% HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
% WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
% FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
% OTHER DEALINGS IN THE SOFTWARE.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Lewis J.}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Pollard}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Engineer} % Career or current job title

	{\huge Games \& Web Developer}
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Sheffield, UK}\\
	\icon{Phone}{12}{+447976905367}\\
	\icon{At}{12}{\href{mailto:lewiji+cv@gmail.com}{lewiji@gmail.com}}\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://sati.stream}{sati.stream}}\\
	\icon{Github}{12}{\href{https://github.com/lewiji}{github.com/lewiji}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/lewis-pollard/}{lewis-pollard}}\\
\end{minipage}

\vspace{0.1cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.54\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	Hacker, tinkerer, open source advocate, full-time Linux user, DOS fan, corporate software engineer by day,
	indie gamedev by night. I've been playing with computers and code since I was 8 years old, gifted with a C64,
	a bunch of tapes, and print magazines full of BASIC code. Today, I'm a professional, proficient, knowledge-hungry
	developer with deep knowledge of my craft, industry best-practice, as well as research, project management and
	agile skills.

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.4\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{Node.js}{90}
		\baritem{C\#}{80}
		\baritem{React}{100}
		\baritem{C++}{70}
		\baritem{Git}{90}
	\end{barchart}
\end{minipage}

\cvsect{Tools}

\begin{center}
	\bubbles{0.618/git, 0.618/Node.js, 0.618/GCP\slash AWS, 0.618/Godot, 0.618/Blender, 0.618/JetBrains IDEs, 0.618/Arch Linux}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Professional Experience}

\begin{entrylist}
	\entry
		{2019 -- Present}
		{Lead Games Developer}
		{Positively Distinctive Media Ltd.}
		{Building the next generation of live participation gameshow content for mobile and desktop using \texttt{node.js},
		\texttt{React}, and \texttt{Next.js}, utilising \texttt{serverless} tech and other scalable platform features via
		\texttt{Google Cloud Platform}. Innovative live, low latency video streaming host and studio-based producer control via
		\texttt{Firebase RTDB} and \texttt{Agora.io}.}
	\entry
		{2016-2019}
		{Senior Software Engineer, HTML5 Games}
		{Spike Games Ltd.}
		{Building \texttt{HTML5} games using \texttt{Phaser.js}, developing and maintaining real-time gaming servers
		 with \texttt{C\# .NET} on  \texttt{AWS EC2}, running \texttt{node.js} game engines and statistical testing software, financial integrations.
		 novel backend gaming solutions on the Funfair platform using \texttt{solidity}.}
	\entry
		{2013-2015}
		{Games Developer}
		{Gaming Realms Plc.}
		{Cross-platform \texttt{HTML5/WebGL} games for the casino industry. Focus on well-architected, modular
		\texttt{Javascript} utilising tools like \texttt{Jenkins}, and libraries such as \texttt{Pixi} and \texttt{Greensock} to reliably deliver cutting-edge HTML5 browser games.}
	\entry
		{2010-2011}
		{Software Engineering Industrial Trainee}
		{IBM UK Ltd}
		{\texttt{MDM Workbench} Development Team, with a focus on \texttt{Java EE}, developing \texttt{Eclipse} tooling and plugins enterprise customer code generation.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2008 -- 2012}
		{BSc Software Engineering with Industrial Placement}
		{Sheffield Hallam University}
		{2:1, including courses in: \texttt{Object-Oriented C++}, \texttt{Networked Software Development},
		\texttt{UNIX, Linux and X},	\texttt{Browser Based Application Design}, \texttt{Case Studies in Software Design},
		\texttt{Applications: Frameworks and Architectures}, and \texttt{Multiplayer and Online Games Development}}
	\entry
		{2006 -- 2008}
		{Computing, Maths and English A-Levels}
		{The Sixth Form College, Solihull}
		{}
	\entry
		{2001 -- 2006}
		{11 GCSEs}
		{Heart of England School, Coventry}
		{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.4\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Personal Projects \& contributions}
	
	\textbf{godotengine} - supporting transition from embedded Mono C\# scripting to .NET 6 coreclr\\
	\textbf{GodotRoguelike} - turn-based roguelike framework for Godot built using C\#\\
	\textbf{RingRogue} - narrative-focused sci-fi climate disaster roguelike played on an abandoned Ringworld full of mutants - with VR support!\\

\end{minipage}
\hfill
\begin{minipage}[t]{0.25\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	Drums, guitar, synths. Indie game development and VR. Adventure and RPG games, traditional roguelikes, interactive fiction. Tabletop games. Bad philosophy, terrible sci-fi and even worse mysticism.
\end{minipage}
\hfill
\begin{minipage}[t]{0.25\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Local projects}
	
	I use AWS community credits to help developer and host local projects, including \href{https://hopeallotment.org.uk/}{HOPE Allotment in Firth Park} and \href{https://forgebakehouse.co.uk/}{Forge Bakehouse} using \texttt{EC2}, \texttt{Route53}, \texttt{Cloudfront}, \texttt{Lambda} and \texttt{SES}.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
